\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-06-05 paper/ms.tex

In \eq{gp-likelihood} the physical parameters of the exoplanet are called
$\bvec{\theta}$ and, in this example, the mean function $\mu_\bvec{\theta}(t)$
is a limb-darkened transit light curve \citep{Mandel:2002} and the parameters
$\bvec{\theta}$ are the orbital period $P_\mathrm{orb}$, the transit duration
$T$, the phase or epoch $t_0$, the impact parameter $b$, the radius of the
planet in units of the stellar radius $R_P/R_\star$, and two parameters
describing the limb-darkening profile of the star
\citep{Claret:2011,Kipping:2013}.
As in \sect{rotation}, we model the stellar variability using a GP model
with a kernel given by \eq{rot-kernel} and fit for the parameters of the
exoplanet $\bvec{\theta}$ and the stellar variability $\bvec{\alpha}$
simultaneously.
\response{The full set of parameters $\bvec{\alpha}$ and $\bvec{\theta}$ are
listed in Table~\ref{tab:example-5-params} along with their priors and the
true values for $\bvec{\theta}$.}

>>>>

In \eq{gp-likelihood} the physical parameters of the exoplanet are called
$\bvec{\theta}$ and, in this example, the mean function $\mu_\bvec{\theta}(t)$
is a limb-darkened transit light curve \citep{Mandel:2002} and the parameters
$\bvec{\theta}$ are the orbital period $P_\mathrm{orb}$, the transit duration
$T$, the phase or epoch $t_0$, the impact parameter $B$, the radius of the
planet in units of the stellar radius $R_P/R_\star$, and two parameters
describing the limb-darkening profile of the star
\citep{Claret:2011,Kipping:2013}.
As in \sect{rotation}, we model the stellar variability using a GP model
with a kernel given by \eq{rot-kernel} and fit for the parameters of the
exoplanet $\bvec{\theta}$ and the stellar variability $\bvec{\alpha}$
simultaneously.
\response{The full set of parameters $\bvec{\alpha}$ and $\bvec{\theta}$ are
listed in Table~\ref{tab:example-5-params} along with their priors and the
true values for $\bvec{\theta}$.}
